\textbf{CMCS 818J Project Final Report}

### 2012-12-18 doc/final_report/draft_report.tex
Adding final report draft

\documentclass[11pt, letterpaper, oneside]{article}
\usepackage{enumerate}
\usepackage{ calc }
\usepackage{ amssymb }

@@

\title{CMCS 818J Project Milestone Report}
\author{Behzad Koosha, Christopher Imbriano}

@@

	A scheme for achieving a streaming authenticated data structure (SADS) was proposed by Papamanthou and Shi \cite{sads}.
	The goal of this project is twofold.
	First, we will implement an example of this data structure and second, we will build an application using the SADS primitive.

@@

	The introduced scheme, streaming authenticated data structure, does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
	\item Independence of prover and verifier : the prover and the verifier update their status independently and with no interaction.
	\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
	\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate}

@@

	We have a few frameworks in mind for this task.
	Two of our options at the moment are EventMachine and Node.js.
	Node.js is a "platform for building fast, scalable network applications" and has been gaining popularity in the Ruby community. http://nodejs.org/
	EventMachine is a "fast, simple event-processing library for Ruby programs."http://rubyeventmachine.com/

@@

	\subsection{Semester Outlook}
		While the ultimate goal of the project is to produce a proof-of-concept application which utilizes a SADS scheme, it is best to set manage expectations.
		Our baseline target for this semester is to complete the first two layers described above, that is the underlying data structure and the SADS scheme primitive.
		Having completed these two components, we can then establish time line during which the proof-of-concept application can be hashed out and developed.
		We hope to leverage the Ruby and broader open-source community by packaging this application, or just the SADS scheme primitive, into a library for others to use and provide feedback.

@@

\begin{thebibliography}{9}
	\bibitem{sads} Elaine Shi, Charalampos Papamanthou \emph{Streaming Authenticated Data Structures}, Date Unknown
\end{thebibliography}

>>>>

\documentclass[11pt, letterpaper, oneside]{article}
\usepackage{enumerate}
\usepackage{ calc }
\usepackage{ amssymb }
\usepackage{graphicx}

@@

\title{\textbf{CMCS 818J Project Final Report}}
\author{Behzad Koosha, Christopher Imbriano}

@@

	In this report we will be describing a scheme for achieving a streaming authenticated data structure (SADS) proposed by Papamanthou and 
	Shi \cite{sads}. The goal of this project is twofold. First, we will be implementing an example of this data
	structure and second, we will be building an application using the SADS primitive.

@@

	In the verifiable computation (VC) problem, a client wishes to compute a complex
	function f on an input x. The client does not trust the server and therefore, would like to
	be able to verify the correctness of the computation without investing too much resources.
	The increasing use of distributed computing over the internet also makes strong servers more commonly 
	available. The growth of outsourcable computation in the form of cloud computing has attracted a renewed
	interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.\\

	The introduced scheme, Streaming Authenticated Data Structure (SADS), does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
	\item Independence of prover and verifier : the prover and the verifier update their status independently and with no interaction.
	\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
	\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate}

	The ultimate goal of the proposed scheme is to build secure protocols that enable the verification of computation
	that is performed by an untrusted resource.\\

	The rest of this paper is organized as follows. We will be describing streaming authenticated data structure 
	goals. Some recent research in streaming verifiable computation will be discussed. We then describe the 
	homomorphic property used in the the SADS scheme. Some definitions will be presented in the following section.
	We present significant features of our implementation afterwards followed by presenting the performance of 
	our investigation. Finally, we conclude our paper by providing some future plans.\\

	\section{A Lattice-based Hash Tree Model}

	The bottomline for the proposed scheme uses Merkle tree structure using a hash function that has the homomorphic
	property. A way to map the outputs to the input domain considers \textit{labels} and allocates the root digest as
	the sum of well defined functions, nameley, \textit{partial digests} applied to the leaves of the Merkle tree.
	This will ease for the felxibility and efficiency in streaming update for the verifier and prover. \\

	Each node in the tree has a label $\lambda$ and a digest \textit{d}, where a node's digest
	could be computed uniquely from its label. Given two children labels, the digest of the parent can be 
	calculated. Figure one represents this property. The labels are denoted by circles and digests are 
	represented with squares. \\

        \begin{figure}[h]
        \centering
        \includegraphics[width=100mm]{./pic/label_digest.jpg}
        \caption[]{Labels and Digests}
        \end{figure}

	As an example, if the set of elements contains the nodes {1,4,6,7} the digest of the hash root of the tree 
	could be expressed as : \textit{D}(1)+\textit{D}(4)+\textit{D}(6)+\textit{D}(7)
        where \textit{D}(x) is the partial digest of the root with respect to x. \\

	The hash function is calculated as follows. Given a security parameter \textit{k}, $\textit{n} = 
	poly(\textit{k})$ and $\textit{q} $, $\textit{$\mu$}$, $\textit{$\beta$}$ outputed parameteres by the SADS 
	algorithm, $\textbf{L}, \textbf{R} \in Z $ two (k $\times$ m) random uniform matrices in \textit{mod q}, the 
	hashed function is defined as h(x,y)= $\textbf{L}$.x + $\textbf{R}$.y mod q. \\

	\section{Properties of Digests and Labels}

	\begin{enumerate}
	\item Having a label of a node, its digest can be computed (not necessarily the other way around)
	\item Having the labels of the two children nodes, using the hash functions, the digest of the parent
	      could be computed.
	\end{enumerate}

	\section{Prover}

	The proof of leaf node \textit{i} consists of: 
	\begin{enumerate}
	 \item the labels of nodes from \textit{i} to the root
	 \item the sibling nodes to that path
	\end{enumerate}

	In figure two, the labels are presented in green (path to the root) while the sibling
	nodes to that path are colored in blue.

	\begin{figure}[h]
        \centering
        \includegraphics[width=100mm]{./pic/8.jpg}
        \caption[]{Prover}
        \end{figure}

	\section{Verifier}

	The verifier computes the digest for every node on the path from \textit{i} to the root in two ways, and checks
	if they are consistent :

	\begin{enumerate}
	 \item using the \textit{labels} of its children
	 \item from the \textit{label} of the node itself
	\end{enumerate}

@@

	%We have a few frameworks in mind for this task.
	%Two of our options at the moment are EventMachine and Node.js.
	%Node.js is a "platform for building fast, scalable network applications" and has been gaining popularity in the Ruby community. http://nodejs.org/
	%EventMachine is a "fast, simple event-processing library for Ruby programs."http://rubyeventmachine.com/

	\section{Simulation outline}

	For the first stage of this project Ruby is used due to the following reasons :

	\begin{enumerate}
	\item built in support of matrix and vector operations
	\item vibrant developer community
	\item possibility for extension in C
        \item numeric and visualization library
	\end{enumerate}

@@

	%\subsection{Semester Outlook}
		%While the ultimate goal of the project is to produce a proof-of-concept application which utilizes a SADS scheme, it is best to set manage expectations.
		%Our baseline target for this semester is to complete the first two layers described above, that is the underlying data structure and the SADS scheme primitive.
		%Having completed these two components, we can then establish time line during which the proof-of-concept application can be hashed out and developed.
		%We hope to leverage the Ruby and broader open-source community by packaging this application, or just the SADS scheme primitive, into a library for others to use and provide feedback.

@@

\begin{thebibliography}{9}
	\bibitem{sads} Elaine Shi, Charalampos Papamanthou \emph{Streaming Authenticated Data Structures}, Date Unknown
	\bibitem{evsc} B. Applebaum, Y. Ishai
and E. Kushilevitz \emph{From Secrecy to Soundness:
Efficient Verification via Secure Computation}
	\end{thebibliography}
